---
title: "Prediction of Breast Mass:  Documentation"
author: "Precious Eunice Grullo"
date: "4/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Dataset
This application use the dataset "BreastCancer" from the "mlbench" r package.  We included only the pertinent variables in the dataset.

```{r, eval=TRUE}
library(mlbench)
data("BreastCancer")
df <- BreastCancer[,-c(1,7)]
str(df)
```
The dataset has 699 observations of 9 variables.  The outcome is the variable "class" which classifies the breast mass as benign or malignant.  The other eight variables are histopathological descriptions made by Dr. William Wolberg, a physician from University of Wisconsin Hospital.  The eight predictor variables are as follows:
-Cl.thickness=Clump Thickness
-Cell.size=Uniformity of Cell Size
-Cell.shape=Uniformity of Cell Shape
-Marg.adhesion=Marginal Adhesion
-Epith.c.size=Single Epithelial Cell Size
-Bare.nuclei=Bare Nuclei
-Bl.cromatin=Bland Chromatin
-Normal.nucleoli=Normal Nucleoli
-Mitoses=Mitoses

#Prediction Model
A prediction model was built using logistic regression.
```{r}
model <- glm(Class~., data=df, family=binomial)
summary(model)
```

The application uses this model to predict the breast mass classification of future tissue specimen.  The user selects the grade of each variable and the application produces an output which classifies the breast mass as "benign" or "malignant".  The server does the following calculation.

```{r, echo=TRUE, eval=FALSE}
model <- glm(Class~., data=df, family=binomial)
breast <- data.frame(Cl.thickness=input$thick,Cell.size=input$size,Cell.shape=input$shape,
          Marg.adhesion=input$margin,Epith.c.size=input$epith,Bl.cromatin=input$chr,
          Normal.nucleoli=input$nuc,Mitoses=input$mit)
pred <- predict(model, newdata=breast, type="response")
predicted <- ifelse(pred>0.5, "malignant", "benign")
predicted
```
-The application is hosted at https://preciouseunice.shinyapps.io/dataproductproject/.
